---
title: "Data Preprocessing"
author: "Jaeeun Ryu"
date: "12/23/2021"
output: pdf_document
---

```{r}
library(dplyr)
```


```{r}
memory.size(max = TRUE)    
memory.size(max = FALSE)   
memory.limit(size = NA)     
memory.limit(size = 50000)  
```

```{r}
#install.packages("doParallel")
library(doParallel)

# Check the number of cores

detectCores()
numCores <- detectCores() -1
cl <- makeCluster(numCores)
registerDoParallel(cl)

```

############################################################
**0. Data back up **
############################################################


```{r}
save(df_full_renew, file = 'D:/EUN/KU/Thesis/RCODE/workspace/df_full_renew.RData')


load('D:/EUN/KU/Thesis/RCODE/workspace/df_full_renew.RData')
```



############################################################
**1. Data importing **
############################################################


```{r}
setwd("D:/EUN/KU/Thesis/RCODE")

df <- read.csv("Loan_status_2007-2020Q3.gzip" ,na.strings=c("NA", ""))


head(df)
dim(df)


# colnames(df)

```

```{r}
cha_df<- df %>% select_if(is.character)
num_df <- df %>% select_if(is.numeric)

# colnames(cha_df)
# colnames(num_df)
```

############################################################
**2. Exploratory Data Analysis **
############################################################

*Target variable*
```{r}
# Use 'Fully Paid' and 'Charged Off' variables as the target variable.
# install.packages("dplyr")
library(dplyr)

df_LC <- df %>% filter(loan_status %in% c('Fully Paid' , 'Charged Off'))
dim(df_LC)
```


*predictor variables*
```{r}
df_LC <- df_LC[ , !colnames(df_LC)%in%
                      c("X", "policy_code",
                        "id", "url", "pymnt_plan","zip_code","issue_d","addr_state", "earliest_cr_line",
                        
                        # 31 variables
                        "collection_recovery_fee", "collections_12_mths_ex_med", "last_credit_pull_d",
                        "last_pymnt_amnt",
                        "last_pymnt_d", "mths_since_last_major_derog", "next_pymnt_d", "out_prncp", "out_prncp_inv",
                        "recoveries", "total_pymnt", "total_pymnt_inv", "total_rec_int", "total_rec_late_fee",
                        "total_rec_prncp", "hardship_flag",
                        "hardship_type", "hardship_reason", "hardship_status", "deferral_term",
                        "hardship_amount", "hardship_start_date", "hardship_end_date", "payment_plan_start_date",
                        "hardship_length", "hardship_dpd", "hardship_loan_status",
                        "orig_projected_additional_accrued_interest", "hardship_payoff_balance_amount",
                        "hardship_last_payment_amount", "debt_settlement_flag" ,"last_fico_range_high","last_fico_range_low",
                        "funded_amnt", "funded_amnt_inv"
                        
                        
                       # "disbursement_method","debt_settlement_flag_date","settlement_status", "settlement_date",
                       # "settlement_amount","settlement_percentage", "settlement_term"
                        
                        
                        
                        
                         )]

dim(df_LC)
```



```{r}
df_LC <- df_LC %>% filter(dti > 0)
dim(df_LC)
```

*rate to numeric*
```{r}


df_LC$int_rate <- as.numeric(gsub('[%]' , '', df_LC$int_rate))
df_LC$revol_util <- as.numeric(gsub('[%]' , '', df_LC$revol_util))
# df_modi$term <- as.numeric(gsub('[months]' , '', df_modi$term))

```

*average fico scores*

```{r}


df_LC$fico_avg <- (df_LC$fico_range_high + df_LC$fico_range_low) / 2
df_LC <- df_LC %>% select(-one_of("fico_range_high","fico_range_low"))


df_LC$sec_app_fico_avg <- (df_LC$sec_app_fico_range_low + df_LC$sec_app_fico_range_high) / 2
df_LC <- df_LC %>% select(-one_of("sec_app_fico_range_low", "sec_app_fico_range_high"))

dim(df_LC)
```

*Remove variables*
```{r}
# grade: use sub_grade (sub-variable of grade)
# title/emp_title/emp_lenght : wide range

vars_to_remove <- 
  c("sub_grade", "title", "emp_title", "emp_length")

df_LC <- df_LC %>% select(-one_of(vars_to_remove))

```

```{r}
# Variables that has more than 90% of one value. 


df_LC <- df_LC[ , !colnames(df_LC)%in%
                      c("acc_now_delinq", "chargeoff_within_12_mths", "tax_liens","delinq_amnt")]

df_LC <- df_LC[ , !colnames(df_LC)%in%
                      c("num_tl_120dpd_2m ", "num_tl_30dpd ", "num_tl_90g_dpd_24m")]

dim(df_LC)
head(df_LC)
```


```{r}
save(df_LC, file = 'D:/EUN/KU/Thesis/RCODE/workspace/df_LC.RData')

load('D:/EUN/KU/Thesis/RCODE/workspace/df_LC.RData')
dim(df_LC)
head(df_LC)
```




############################################################
**Full dataset **
############################################################


```{r}
df_full <- df_LC[, colSums(is.na(df_LC)) == 0]
dim(df_full)
head(df_full)
```


```{r}
save(df_full, file = 'D:/EUN/KU/Thesis/RCODE/workspace/df_full.RData')

load('D:/EUN/KU/Thesis/RCODE/workspace/df_full.RData')

dim(df_full)
```


```{r}

df_full$loan_status <- as.numeric(ifelse(df_full$loan_status == 'Fully Paid' , 1, 0) )

cat('Fully Paid: ', (nrow(df_full %>% filter(df_full$loan_status == 1)) / nrow(df_full)))
cat('\nCharged Off: ', nrow(df_full %>% filter(df_full$loan_status == 0)) / nrow(df_full))

```

```{r}

library(caret)

# One-hot Encoding

dmy <- dummyVars(~., data = df_full)
df_full <- data.frame(predict(dmy, newdata = df_full))

dim(df_full)
head(df_full)
```

############################################################
**missing variables**
############################################################




```{r}

as.integer(nrow(df_LC) * 0.1)

```


```{r}

# Remain the variables which contain the missing values under 0.01

df_imp <- df_LC[ ,colSums(is.na(df_LC)) <= as.integer(nrow(df_LC) * 0.1)]

dim(df_imp)
```


```{r}

df_na <- df_imp[, colSums(is.na(df_imp)) !=0 ]
as.data.frame(colSums(is.na(df_na)))

na_col<- c(colnames(is.na(df_na)))

dim(df_na)  # Impputated variables: 35

```

```{r}
int <- df_na %>% select_if(is.integer)
num <- df_na %>% select_if(is.double)

```


```{r}
for (i in 1:ncol(df_imp)) {
  if (class(df_imp[, i]) == 'integer'){
    df_imp[, i][is.na(df_imp[,i])] <- as.integer(mean(df_imp[, i], na.rm = TRUE))  
  }
  else if (class(df_imp[, i]) == 'numeric'){
    df_imp[, i][is.na(df_imp[,i])] <- round(mean(df_imp[, i], na.rm = TRUE),2)
  }
  
}
```


```{r}
dplyr::count(df_imp, dti, sort = TRUE)

```


```{r}
dim(df_imp)
```

```{r}
save(df_imp, file = 'D:/EUN/KU/Thesis/RCODE/workspace/df_imp.RData')

load('D:/EUN/KU/Thesis/RCODE/workspace/df_imp.RData')

dim(df_imp)
```

```{r}

df_imp$loan_status <- as.numeric(ifelse(df_imp$loan_status == 'Fully Paid' , 1, 0) )

cat('Fully Paid: ', (nrow(df_imp %>% filter(df_imp$loan_status == 1)) / nrow(df_imp)))
cat('\nCharged Off: ', nrow(df_imp %>% filter(df_imp$loan_status == 0)) / nrow(df_imp))


```

```{r}

library(caret)

# One-hot Encoding

dmy <- dummyVars(~., data = df_imp)
df_imp <- data.frame(predict(dmy, newdata = df_imp))

dim(df_imp)
head(df_imp)
```

############################################################
**log scale **
############################################################


############################################################
**3. Data Preprocessing **
############################################################


############################################################
**outliers **
############################################################

```{r}
# pub_rec

pub_rec_modi <- df_full %>% filter(df_full$pub_rec <= 3)
nrow(pub_rec_modi)/ nrow(df_full)

df_full[(df_full$pub_rec > 3), 'pub_rec'] = 3

dplyr::count(df_full, pub_rec, sort = TRUE)
```



```{r}
# delinq_2yrs

delinq_2yrs_modi <- df_full %>% filter(df_full$delinq_2yrs <= 4)
nrow(delinq_2yrs_modi)/ nrow(df_full)

df_full[(df_full$delinq_2yrs > 4), 'delinq_2yrs'] = 4

dplyr::count(df_full, delinq_2yrs, sort = TRUE)
```

```{r}
# dti

dti_modi <- df_full %>% filter(df_full$dti <= 50)
nrow(dti_modi)/ nrow(df_full)

df_full <- df_full %>% filter(df_full$dti <= 50)

dim(df_full)

```

```{r}
# annual_inc

annual_inc_modi <- df_full %>% filter(df_full$annual_inc <= 300000)
nrow(annual_inc_modi)/ nrow(df_full)

df_full <- df_full %>% filter(df_full$annual_inc <= 300000)

dim(df_full)

```

```{r}
# open_acc

open_acc_modi <- df_full %>% filter(df_full$open_acc <= 40)
nrow(open_acc_modi)/ nrow(df_full)

df_full <- df_full %>% filter(df_full$open_acc <= 40)

dim(df_full)

```

```{r}
# total_acc

total_acc_modi <- df_full %>% filter(df_full$total_acc <= 80)
nrow(total_acc_modi)/ nrow(df_full)

df_full <- df_full %>% filter(df_full$total_acc <= 80)

dim(df_full)

```

```{r}
# revol_bal

revol_bal_modi <- df_full %>% filter(df_full$revol_bal <= 100000)
nrow(revol_bal_modi)/ nrow(df_full)

df_full <- df_full %>% filter(df_full$revol_bal <= 100000)

dim(df_full)

```

```{r}
colnames(df_imp)
```

*Graph*
```{r}
qqnorm(df_imp$revol_bal_log)
qqline(df_imp$revol_bal_log)
```



```{r}
df_imp %>%
  ggplot(aes(revol_bal)) +
  geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity')
```



```{r}
df_imp$int_rate_log <- log(df_imp$int_rate + 1)
```

```{r}
df_imp %>%
  ggplot(aes(num_actv_bc_tl_log)) +
  geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity')
```

*log_scaled variables*

```{r}
# 28 variables
log_scale <- c("annual_inc", "avg_cur_bal", "dti", "int_rate", 
    "mo_sin_rcnt_tl",  "mths_since_recent_bc", 
    "num_actv_bc_tl", "num_il_tl", "revol_bal", "open_acc", "revol_util",
    "total_acc", "tot_cur_bal", "total_rev_hi_lim", "acc_open_past_24mths", "bc_open_to_buy",
    "mo_sin_rcnt_rev_tl_op", "num_actv_rev_tl", "num_bc_sats",  "num_op_rev_tl", 
    "num_rev_accts", "num_rev_tl_bal_gt_0", "num_sats", "num_tl_op_past_12m", "tot_hi_cred_lim",
    "total_bal_ex_mort", "total_bc_limit", "total_il_high_credit_limit")

length(log_scale)
```


```{r}

df_logs <- df_imp %>%
    mutate(across(
        .cols = contains(log_scale),
        .fns = log1p)) %>% 
    rename_with(.cols = contains(log_scale),
                .fn = ~paste0(., '_log'))

dim(df_logs)
head(df_logs)

```

```{r}
colSums(is.na(df_logs))
```

```{r}
count(df_logs, dti_log)
```

```{r}
save(df_logs, file = 'D:/EUN/KU/Thesis/RCODE/workspace/df_logs.RData')

load('D:/EUN/KU/Thesis/RCODE/workspace/df_logs.RData')
dim(df_logs)
```

```{r}

library(dplyr)

df_logs$loan_status <- as.numeric(ifelse(df_logs$loan_status == 'Fully Paid' , 1, 0) )

cat('Fully Paid: ', (nrow(df_logs %>% filter(df_logs$loan_status == 1)) / nrow(df_logs)))
cat('\nCharged Off: ', nrow(df_logs %>% filter(df_logs$loan_status == 0)) / nrow(df_logs))

```

```{r}

library(caret)

# One-hot Encoding

dmy <- dummyVars(~., data = df_logs)
df_logs <- data.frame(predict(dmy, newdata = df_logs))

dim(df_logs)
head(df_logs)
```


############################################################
**Coefficiency**
############################################################

```{r}
num_vars <- 
  df_logs %>% 
  sapply(is.numeric) %>% 
  which() %>% 
  names()


res <- cor(df_logs[, num_vars])
round(res, 2)
```

```{r}

cor_col_0.5 <- caret::findCorrelation(res, names = TRUE, cutoff = 0.5, exact = TRUE) #27
cor_col_0.6 <- caret::findCorrelation(res, names = TRUE, cutoff = 0.6, exact = TRUE) #21
cor_col_0.7 <- caret::findCorrelation(res, names = TRUE, cutoff = 0.7, exact = TRUE) #15
cor_col_0.9 <- caret::findCorrelation(res, names = TRUE, cutoff = 0.9, exact = TRUE) #5

```


```{r}
vars_to_remove <- cor_col_0.5
cor_col_0.5 <- df_logs %>% select(-one_of(vars_to_remove))

vars_to_remove <- cor_col_0.6
cor_col_0.6 <- df_logs %>% select(-one_of(vars_to_remove))

vars_to_remove <- cor_col_0.7
cor_col_0.7 <- df_logs %>% select(-one_of(vars_to_remove))

vars_to_remove <- cor_col_0.9
cor_col_0.9 <- df_logs %>% select(-one_of(vars_to_remove))

dim(cor_col_0.5)
dim(cor_col_0.6)
dim(cor_col_0.7)
dim(cor_col_0.9)

```

```{r}
head(cor_col_0.9)
```

```{r}
save(cor_col_0.5, file = 'D:/EUN/KU/Thesis/RCODE/workspace/cor_col_0.5.RData')
save(cor_col_0.6, file = 'D:/EUN/KU/Thesis/RCODE/workspace/cor_col_0.6.RData')
save(cor_col_0.7, file = 'D:/EUN/KU/Thesis/RCODE/workspace/cor_col_0.7.RData')
save(cor_col_0.9, file = 'D:/EUN/KU/Thesis/RCODE/workspace/cor_col_0.9.RData')

load('D:/EUN/KU/Thesis/RCODE/workspace/cor_col_0.5.RData')
load('D:/EUN/KU/Thesis/RCODE/workspace/cor_col_0.6.RData')
load('D:/EUN/KU/Thesis/RCODE/workspace/cor_col_0.7.RData')
load('D:/EUN/KU/Thesis/RCODE/workspace/cor_col_0.9.RData')


head(cor_col_0.7)
```

```{r}

cor_col_0.6$loan_status <- as.numeric(ifelse(cor_col_0.6$loan_status == 'Fully Paid' , 1, 0) )

cat('Fully Paid: ', (nrow(cor_col_0.6 %>% filter(cor_col_0.6$loan_status == 1)) / nrow(cor_col_0.6)))
cat('\nCharged Off: ', nrow(cor_col_0.6 %>% filter(cor_col_0.6$loan_status == 0)) / nrow(cor_col_0.6))

```

```{r}

library(caret)

# One-hot Encoding

dmy <- dummyVars(~., data = cor_col_0.6)
cor_col_0.6 <- data.frame(predict(dmy, newdata = cor_col_0.6))

dim(cor_col_0.6)
head(cor_col_0.6)
```



###################################################################################################################


##### Full Dataset #####
```{r}

require(caTools)
library(ROSE)
library(ncvreg)
library(pROC)

opt_lambda_scad_full <- c()
Accuracy <- c()
F1 <-c()
AUC <- c()
Sensitivity <- c()
Specificity<- c()
Precision <- c()
Recall <- c()

  for (i in 1:20){
  set.seed(i)
  sample = sample.split(df_full$loan_status, SplitRatio = .70)
  train = subset(df_full, sample == TRUE)
  test  = subset(df_full, sample == FALSE)

  
  X_train = train[ , !colnames(train) %in% 'loan_status']
  y_train = train['loan_status']
  X_test = test[ , !colnames(train) %in% 'loan_status'] 
  y_test = test['loan_status']
  
  cv_scad <- cv.ncvreg(X_train, as.factor(y_train$loan_status), family = 'binomial'
                     , penalty = 'SCAD', gamma = 3.7, returnX = TRUE ,nfolds = 5 )
  
  
  opt_lambda_scad_full[i] <- cv_scad$lambda.min
  
  
  model_scad <- ncvreg(X_train, as.factor(y_train$loan_status), 
                     family = 'binomial', penalty = 'SCAD', gamma = 3.7, returnX = TRUE 
                     , lambda = opt_lambda_scad_full[i])
  
  
  pred_scad <- predict(model_scad, as.matrix(X_test), type = 'class')
  
  CM <- confusionMatrix(as.factor(pred_scad), as.factor(y_test$loan_status), mode = "everything", positive = "0")
  roc_auc <- roc(as.factor(y_test$loan_status), as.numeric(pred_scad))
  
  Accuracy[i] <- CM$overall["Accuracy"]
  
  F1[i] <- CM$byClass["F1"]
  Sensitivity[i] <- CM$byClass["Sensitivity"]
  Specificity[i] <- CM$byClass["Specificity"]
  Precision[i] <- CM$byClass["Precision"]
  Recall[i] <- CM$byClass["Recall"]
  
  AUC[i] <- roc_auc$auc
  }

head(opt_lambda_scad_full)
full_scad_result <- cbind(Accuracy, F1, AUC, Sensitivity, Specificity, Precision, Recall)

```

```{r}
save(opt_lambda_scad_full, file = 'D:/EUN/KU/Thesis/RCODE/workspace/opt_lambda_scad_full.RData')
save(full_scad_result, file = 'D:/EUN/KU/Thesis/RCODE/workspace/full_scad_result.RData')
```

```{r}
round(colMeans(full_scad_result)*100, 2)
round(apply(full_scad_result, 2, sd)/sqrt(20)*100 , 2)
```

##### Imputation Dataset #####
```{r}

require(caTools)
library(ROSE)
library(ncvreg)
library(pROC)

opt_lambda_scad_imp <- c()
Accuracy <- c()
F1 <-c()
AUC <- c()

  for (i in 1:20){
  set.seed(i)
  sample = sample.split(df_imp$loan_status, SplitRatio = .70)
  train = subset(df_imp, sample == TRUE)
  test  = subset(df_imp, sample == FALSE)

  
  X_train = train[ , !colnames(train) %in% 'loan_status']
  y_train = train['loan_status']
  X_test = test[ , !colnames(train) %in% 'loan_status'] 
  y_test = test['loan_status']
  
  cv_scad <- cv.ncvreg(X_train, as.factor(y_train$loan_status), family = 'binomial'
                     , penalty = 'SCAD', gamma = 3.7, returnX = TRUE ,nfolds = 5 )
  
  
  opt_lambda_scad_imp[i] <- cv_scad$lambda.min
  
  
  model_scad <- ncvreg(X_train, as.factor(y_train$loan_status), 
                     family = 'binomial', penalty = 'SCAD', gamma = 3.7, returnX = TRUE 
                     , lambda = opt_lambda_scad_imp[i])
  
  
  pred_scad <- predict(model_scad, as.matrix(X_test), type = 'class')
  
  CM <- confusionMatrix(as.factor(pred_scad), as.factor(y_test$loan_status), mode = "everything", positive = "0")
  roc_auc <- roc(as.factor(y_test$loan_status), as.numeric(pred_scad))
  
  Accuracy[i] <- CM$overall["Accuracy"]
  F1[i] <- CM$byClass['F1']
  AUC[i] <- roc_auc$auc
  }

head(opt_lambda_scad_imp)
imp_scad_result <- cbind(Accuracy, F1, AUC)

```

```{r}
save(opt_lambda_scad_imp, file = 'D:/EUN/KU/Thesis/RCODE/workspace/opt_lambda_scad_imp.RData')
save(imp_scad_result, file = 'D:/EUN/KU/Thesis/RCODE/workspace/imp_scad_result.RData')
```

```{r}
round(colMeans(imp_scad_result)*100, 4)
round(apply(imp_scad_result, 2, sd)/sqrt(20)*100 , 4)
```

##### log-scaled Dataset #####

```{r}

require(caTools)
library(ROSE)
library(ncvreg)
library(pROC)

opt_lambda_scad_logs <- c()
Accuracy <- c()
F1 <-c()
AUC <- c()

  for (i in 1:20){
  set.seed(i)
  sample = sample.split(df_logs$loan_status, SplitRatio = .70)
  train = subset(df_logs, sample == TRUE)
  test  = subset(df_logs, sample == FALSE)

  
  X_train = train[ , !colnames(train) %in% 'loan_status']
  y_train = train['loan_status']
  X_test = test[ , !colnames(train) %in% 'loan_status'] 
  y_test = test['loan_status']
  
  cv_scad <- cv.ncvreg(X_train, as.factor(y_train$loan_status), family = 'binomial'
                     , penalty = 'SCAD', gamma = 3.7, returnX = TRUE ,nfolds = 5 )
  
  
  opt_lambda_scad_logs[i] <- cv_scad$lambda.min
  
  
  model_scad <- ncvreg(X_train, as.factor(y_train$loan_status), 
                     family = 'binomial', penalty = 'SCAD', gamma = 3.7, returnX = TRUE 
                     , lambda = opt_lambda_scad_logs[i])
  
  
  pred_scad <- predict(model_scad, as.matrix(X_test), type = 'class')
  
  CM <- confusionMatrix(as.factor(pred_scad), as.factor(y_test$loan_status), mode = "everything", positive = "0")
  roc_auc <- roc(as.factor(y_test$loan_status), as.numeric(pred_scad))
  
  Accuracy[i] <- CM$overall["Accuracy"]
  F1[i] <- CM$byClass['F1']
  AUC[i] <- roc_auc$auc
  }

head(opt_lambda_scad_logs)
logs_scad_result <- cbind(Accuracy, F1, AUC)

```

```{r}
save(opt_lambda_scad_logs, file = 'D:/EUN/KU/Thesis/RCODE/workspace/opt_lambda_scad_logs.RData')
save(logs_scad_result, file = 'D:/EUN/KU/Thesis/RCODE/workspace/logs_scad_result.RData')


```

```{r}
round(colMeans(logs_scad_result)*100, 4)
round(apply(logs_scad_result, 2, sd)/sqrt(20)*100 , 4)
```

##### cor_col_0.5 Dataset #####

```{r}

require(caTools)
library(ROSE)
library(ncvreg)
library(pROC)

opt_lambda_scad_cor_0.5 <- c()
Accuracy <- c()
F1 <-c()
AUC <- c()

  for (i in 1:20){
  set.seed(i)
  sample = sample.split(cor_col_0.5$loan_status, SplitRatio = .70)
  train = subset(cor_col_0.5, sample == TRUE)
  test  = subset(cor_col_0.5, sample == FALSE)

  
  X_train = train[ , !colnames(train) %in% 'loan_status']
  y_train = train['loan_status']
  X_test = test[ , !colnames(train) %in% 'loan_status'] 
  y_test = test['loan_status']
  
  cv_scad <- cv.ncvreg(X_train, as.factor(y_train$loan_status), family = 'binomial'
                     , penalty = 'SCAD', gamma = 3.7, returnX = TRUE ,nfolds = 5 )
  
  
  opt_lambda_scad_cor_0.5[i] <- cv_scad$lambda.min
  
  
  model_scad <- ncvreg(X_train, as.factor(y_train$loan_status), 
                     family = 'binomial', penalty = 'SCAD', gamma = 3.7, returnX = TRUE 
                     , lambda = opt_lambda_scad_cor_0.5[i])
  
  
  pred_scad <- predict(model_scad, as.matrix(X_test), type = 'class')
  
  CM <- confusionMatrix(as.factor(pred_scad), as.factor(y_test$loan_status), mode = "everything", positive = "0")
  roc_auc <- roc(as.factor(y_test$loan_status), as.numeric(pred_scad))
  
  Accuracy[i] <- CM$overall["Accuracy"]
  F1[i] <- CM$byClass['F1']
  AUC[i] <- roc_auc$auc
  }

head(opt_lambda_scad_cor_0.5)
cor_0.5_scad_result <- cbind(Accuracy, F1, AUC)

```

```{r}
save(opt_lambda_scad_cor_0.5, file = 'D:/EUN/KU/Thesis/RCODE/workspace/opt_lambda_scad_cor_0.5.RData')
save(cor_0.5_scad_result, file = 'D:/EUN/KU/Thesis/RCODE/workspace/cor_0.5_scad_result.RData')
```

```{r}
round(colMeans(cor_0.5_scad_result)*100, 4)
round(apply(cor_0.5_scad_result, 2, sd)/sqrt(20)*100 , 4)
```

##### cor_col_0.6 Dataset #####

```{r}

require(caTools)
library(ROSE)
library(ncvreg)
library(pROC)

opt_lambda_scad_cor_0.6 <- c()
Accuracy <- c()
F1 <-c()
AUC <- c()

  for (i in 1:20){
  set.seed(i)
  sample = sample.split(cor_col_0.6$loan_status, SplitRatio = .70)
  train = subset(cor_col_0.6, sample == TRUE)
  test  = subset(cor_col_0.6, sample == FALSE)

  
  X_train = train[ , !colnames(train) %in% 'loan_status']
  y_train = train['loan_status']
  X_test = test[ , !colnames(train) %in% 'loan_status'] 
  y_test = test['loan_status']
  
  cv_scad <- cv.ncvreg(X_train, as.factor(y_train$loan_status), family = 'binomial'
                     , penalty = 'SCAD', gamma = 3.7, returnX = TRUE ,nfolds = 5 )
  
  
  opt_lambda_scad_cor_0.6[i] <- cv_scad$lambda.min
  
  
  model_scad <- ncvreg(X_train, as.factor(y_train$loan_status), 
                     family = 'binomial', penalty = 'SCAD', gamma = 3.7, returnX = TRUE 
                     , lambda = opt_lambda_scad_cor_0.6[i])
  
  
  pred_scad <- predict(model_scad, as.matrix(X_test), type = 'class')
  
  CM <- confusionMatrix(as.factor(pred_scad), as.factor(y_test$loan_status), mode = "everything", positive = "0")
  roc_auc <- roc(as.factor(y_test$loan_status), as.numeric(pred_scad))
  
  Accuracy[i] <- CM$overall["Accuracy"]
  F1[i] <- CM$byClass['F1']
  AUC[i] <- roc_auc$auc
  }

head(opt_lambda_scad_cor_0.6)
cor_0.6_scad_result <- cbind(Accuracy, F1, AUC)

```


```{r}
save(opt_lambda_scad_cor_0.6, file = 'D:/EUN/KU/Thesis/RCODE/workspace/opt_lambda_scad_cor_0.6.RData')
save(cor_0.6_scad_result, file = 'D:/EUN/KU/Thesis/RCODE/workspace/cor_0.6_scad_result.RData')
```

```{r}
round(colMeans(cor_0.6_scad_result)*100, 4)
round(apply(cor_0.6_scad_result, 2, sd)/sqrt(20)*100 , 4)
```

##### cor_col_0.7 Dataset #####

```{r}

require(caTools)
library(ROSE)
library(ncvreg)
library(pROC)

opt_lambda_scad_cor_0.7 <- c()
Accuracy <- c()
F1 <-c()
AUC <- c()

  for (i in 1:20){
  set.seed(i)
  sample = sample.split(cor_col_0.7$loan_status, SplitRatio = .70)
  train = subset(cor_col_0.7, sample == TRUE)
  test  = subset(cor_col_0.7, sample == FALSE)

  
  X_train = train[ , !colnames(train) %in% 'loan_status']
  y_train = train['loan_status']
  X_test = test[ , !colnames(train) %in% 'loan_status'] 
  y_test = test['loan_status']
  
  cv_scad <- cv.ncvreg(X_train, as.factor(y_train$loan_status), family = 'binomial'
                     , penalty = 'SCAD', gamma = 3.7, returnX = TRUE ,nfolds = 5 )
  
  
  opt_lambda_scad_cor_0.7[i] <- cv_scad$lambda.min
  
  
  model_scad <- ncvreg(X_train, as.factor(y_train$loan_status), 
                     family = 'binomial', penalty = 'SCAD', gamma = 3.7, returnX = TRUE 
                     , lambda = opt_lambda_scad_cor_0.7[i])
  
  
  pred_scad <- predict(model_scad, as.matrix(X_test), type = 'class')
  
  CM <- confusionMatrix(as.factor(pred_scad), as.factor(y_test$loan_status), mode = "everything", positive = "0")
  roc_auc <- roc(as.factor(y_test$loan_status), as.numeric(pred_scad))
  
  Accuracy[i] <- CM$overall["Accuracy"]
  F1[i] <- CM$byClass['F1']
  AUC[i] <- roc_auc$auc
  }

head(opt_lambda_scad_cor_0.7)
cor_0.7_scad_result <- cbind(Accuracy, F1, AUC)

```

```{r}
save(opt_lambda_scad_cor_0.7, file = 'D:/EUN/KU/Thesis/RCODE/workspace/opt_lambda_scad_cor_0.7.RData')
save(cor_0.7_scad_result, file = 'D:/EUN/KU/Thesis/RCODE/workspace/cor_0.7_scad_result.RData')
```

```{r}
round(colMeans(cor_0.7_scad_result)*100, 4)
round(apply(cor_0.7_scad_result, 2, sd)/sqrt(20)*100 , 4)
```

##### cor_col_0.9 Dataset #####

```{r}

require(caTools)
library(ROSE)
library(ncvreg)
library(pROC)

opt_lambda_scad_cor_0.9 <- c()
Accuracy <- c()
F1 <-c()
AUC <- c()

  for (i in 1:20){
  set.seed(i)
  sample = sample.split(cor_col_0.9$loan_status, SplitRatio = .70)
  train = subset(cor_col_0.9, sample == TRUE)
  test  = subset(cor_col_0.9, sample == FALSE)

  
  X_train = train[ , !colnames(train) %in% 'loan_status']
  y_train = train['loan_status']
  X_test = test[ , !colnames(train) %in% 'loan_status'] 
  y_test = test['loan_status']
  
  cv_scad <- cv.ncvreg(X_train, as.factor(y_train$loan_status), family = 'binomial'
                     , penalty = 'SCAD', gamma = 3.7, returnX = TRUE ,nfolds = 5 )
  
  
  opt_lambda_scad_cor_0.9[i] <- cv_scad$lambda.min
  
  
  model_scad <- ncvreg(X_train, as.factor(y_train$loan_status), 
                     family = 'binomial', penalty = 'SCAD', gamma = 3.7, returnX = TRUE 
                     , lambda = opt_lambda_scad_cor_0.9[i])
  
  
  pred_scad <- predict(model_scad, as.matrix(X_test), type = 'class')
  
  CM <- confusionMatrix(as.factor(pred_scad), as.factor(y_test$loan_status), mode = "everything", positive = "0")
  roc_auc <- roc(as.factor(y_test$loan_status), as.numeric(pred_scad))
  
  Accuracy[i] <- CM$overall["Accuracy"]
  F1[i] <- CM$byClass['F1']
  AUC[i] <- roc_auc$auc
  }

head(opt_lambda_scad_cor_0.9)
cor_0.9_scad_result <- cbind(Accuracy, F1, AUC)

```

```{r}
save(opt_lambda_scad_cor_0.9, file = 'D:/EUN/KU/Thesis/RCODE/workspace/opt_lambda_scad_cor_0.9.RData')
save(cor_0.9_scad_result, file = 'D:/EUN/KU/Thesis/RCODE/workspace/cor_0.9_scad_result.RData')
```

```{r}
round(colMeans(cor_0.9_scad_result)*100, 4)
round(apply(cor_0.9_scad_result, 2, sd)/sqrt(20)*100 , 4)
```


